---
title: "hw6"
author: "Autumn Li UNI:ql2280"
date: "11/7/2016"
output: pdf_document
---
#Part 1: Inverse Transform Method
1. Define a function f which takes three inputs x, a vector, and scalars a and xmin having default values of a = aˆ and xmin = $407, 760. 
```{r}
report <- read.csv("~/Desktop/report.csv", header=FALSE)
report = report[-1,]
x.min = 407760
a.hat = 2.654
x = c(407760:1000000)
f = function (x,x.min = x.min, a.hat = a.hat){
  result = ((a.hat - 1)/x.min)*((x/x.min)^-a.hat)
  return(result)
  }
ans = f(x,x.min,a.hat)
plot(x,ans,main = "function between xmin and 1000000",ylab = "estimated value",xlab = "value between xmin and 1000000")
```
2. For x > xmin, the cdf equals
```{r}
u = 0.5
upper.income = function (u = u,x.min = 407760,a = 2.654 ){
  result = (1-u)^(1/(1-a))*x.min
  return(result)
  }
upper.income(0.5)
```
3. Using the Inverse Transform Method
```{r}
x = runif(1000)
result.1 = upper.income(x)
ans.1 = f(result.1,x.min,a.hat)
hist(ans.1,main = "Estimated value of Pareto distribution", xlab = "1000 simulated draw")

```
4. Using your simulated set, estimate the median income for the richest 1% of the world.
```{r}
result.1 = upper.income(x)
result.2 = median(result.1);result.2
upper.income(0.5)
```
#Part 2: Reject-Accept Method
5. Write a function f that takes as input a vector x and returns a vector of f(x) values.
```{r}
x = c(-3:3)
f <- function(x) {
  return(ifelse((x <= -1 | x >= 3), 0, 1/9*(4-x^2))) 
  }
plot(x,f(x),xlimylab = "Estimated value",xlab =" X",type = "l")
lines(f(x))
```
6. Determine the maximum of f(x) and find an envelope function e(x) by using a uniform density for g(x).
```{r}
xmax = 0
f.max = 4/9
e <- function(x) {
  return(ifelse((x <= -1 | x > 3), Inf, f.max)) }
e(x)
```
7. Using the Accept-Reject Algorithm
```{r}
n.samps <- 1000
n <- 0  
samps <- numeric(n.samps)
while (n < n.samps) {
  y <- runif(1,-3,3)
  u = runif(1)
  if (u < f(y)/e(y)) {
    n <-n+1
    samps[n] <- y
    }
  }
```
8. Plot a histogram of your simulated data with the density function f overlaid in the graph. Label your plot appropriately.
```{r}
x <- seq(0, 1, length = 100)
hist(samps, prob = T, xlim=c(-3,3),ylab = "f(x)", xlab = "x",main = "Histogram of draws from f(x)")
lines(x, f(x),col = "red")
```
#Part 3: Simulation with Built-in R Functions
9. Write a while() loop to implement this procedure.
```{r}
x.start = 5
n.1 = 1
x.vals =NULL
while(x.start > 0) {
  r = runif(1,min = -2, max = 1)
  x.start= x.start + r
  x.vals[n.1] = x.start
  n.1 = n.1 +1
  }
x.vals
n.1
```
10. Produce a plot of the random walk values x.vals from above versus the iteration number. 
```{r}
plot(c(1:(n.1-1)),x.vals,xlab = "Iteration Number",ylab = "x.values")
lines(x.vals)
```
11. Write a function random.walk() to perform the random walk procedure that you implemented in question (9)
```{r}
random.walk = function (x.start = 5, plot.walk = TRUE){
  x.vals =NULL
  n.1 = 1
  while(x.start > 0) {
    r = runif(1,min = -2, max = 1)
    x.start= x.start + r
    x.vals[n.1] = x.start
    n.1 = n.1 +1
    }
  num.steps = c(1:(n.1-1))
  result = list(x.vals,num.steps)
  if(plot.walk ==TRUE){
    plot(num.steps,x.vals)
    lines(x.vals)
    }
  return(result)
  }
random.walk(x.start = 5, plot.walk = TRUE)
random.walk(x.start = 10, plot.walk = FALSE)
```
12. We’d like to answer the following question using simulation
```{r}
rep = 10000
num = NULL
for (i in 1:rep){
  num[i] = max(unlist(random.walk(x.start = 5, plot.walk = FALSE)[2]))
}
avg_rep = mean(num);avg_rep
```
13. Modify your function random.walk() defined previously so that it takes an additional argument seed
```{r}
set.seed(NULL)
random.walk(x.start = 5, plot.walk = TRUE)
set.seed(NULL)
random.walk(x.start = 10, plot.walk = FALSE)
set.seed(33)
random.walk(x.start = 5, plot.walk = TRUE)
set.seed(33)
random.walk(x.start = 10, plot.walk = FALSE)
```