---
title: "HW 2"
author: "Autumn Li and UNI ql2280"
date: "Oct,03 2016"
output: html_document
---

#Part 1: Loading and Cleaning the Data in R
i. Load the data into a dataframe called housing.
ii. How many rows and columns does the dataframe have?
```{r}
data2 = "~/Desktop/2016 fall/5206/hw2/NYChousing.csv"
housing = read.csv(file = data2, head=TRUE)
nrow = dim(housing)[1];nrow
ncol = dim(housing)[2];ncol
View(housing)

#There are 2506 rows and 22 columns in the data set.
```
iii. Run this command, and explain, in words, what this does:
```{r}
apply(is.na(housing), 2, sum)

#Determing the number of the NA, and then calculating the sum of NA in each column.

```
iv. Remove the rows of the dataset for which the variable Value is NA.
```{r}
housing2 = housing[complete.cases(housing),]
```
v. How many rows did you remove with the previous call? Does this agree with your result from (iii)?
```{r}
#Number of rows deleted
dim(housing)[1]-dim(housing2)[1]
#Total number of NA in all columns
sum(apply(is.na(housing), 2, sum))

#I deleted 1876 rows with the previous call, the total number of NA in all columns is 1970.It is different with the result from part (iii)
#The reason is that some rows has more than 1 NA, however, we delete the row as long as it has an NA.

```

vi. Create a new variable in the dataset called logValue that is equal to the logarithm of the property’s Value.
```{r}
value2 = housing2$Value
logValue=log(value2)
summary(logValue)
```
vii. Create a new variable in the dataset called logUnits that is equal to the logarithm of the number of units in the property. 

```{r}
UnitCount1 = housing2$UnitCount
logUnits = log(UnitCount1)
```
viii. Finally create a new variable in the dataset called after1950 which equals TRUE

```{r}
after1950=housing2$YearBuilt>=1950
housing3=cbind(housing2,after1950)
```
#Part 2: EDA
i. Plot property logValue against property logUnits.
```{r,echo = FALSE}
plot(logValue~logUnits)
```

ii. Makethesameplotasabove,but now include the argument col = factor(housing$after1950).
```{r}
plot(logValue~logUnits,col = factor(housing3$after1950))
legend("bottomright", legend = levels(factor(housing3$after1950)), fill = unique(factor(housing3$after1950)))

#From the plot above, we can tell clearly that which poine is the "YearBuilt after 1950". The red point is the buidling built after 1950.
```

iii. The cor() function calculates the correlation coefficient between two variables.
```{r}
#(i) the whole data
cor(logValue,logUnits)
#(ii) just Manhattan
Borough = housing3$Borough
cor(logValue[Borough=="Manhattan"],logUnits[Borough=="Manhattan"])
#(iii) just Brooklyn
cor(logValue[Borough=="Brooklyn"],logUnits[Borough=="Brooklyn"])
#(iv) for properties built after 1950
cor(logValue[after1950=="TRUE"],logUnits[after1950=="TRUE"])
#(v) for properties built before 1950
cor(logValue[after1950=="FALSE"],logUnits[after1950=="FALSE"])
```

iv. Make two plots showing property logValue against property logUnits for Manhattan and Brooklyn.
```{r}
par(mfrow=c(1,2))
plot(logValue[Borough=="Manhattan"],logUnits[Borough=="Manhattan"],xlab="logUnits",ylab ="log value",main = "Manhattan")
plot(logValue[Borough=="Brooklyn"],logUnits[Borough=="Brooklyn"],xlab="logUnits",ylab ="log value",main = "Brooklyn")

```

v. Consider the following block of code.
```{r}
median(housing3$Value[Borough=="Manhattan"])

#The block of cose has the function to calculate the median value of the Manhattan
```

vi. Make side-by-side box plots comparing property logValue across the five boroughs.
```{r}
par(mfrow=c(1,1))
boxplot(logValue~housing3$Borough,data = housing3)
```

vii. For five boroughs, what are the median property values?
```{r}
median(housing3$Value[Borough=="Manhattan"])
median(housing3$Value[Borough=="Bronx"])
median(housing3$Value[Borough=="Brooklyn"])
median(housing3$Value[Borough=="Queens"])
median(housing3$Value[Borough=="Staten Island"])
```
