---
title: "HW 3"
author: "Autumn Li and UNI ql2280"
date: "October 09, 2016"
output: html_document
---
#i. Use the readLines() command we studied in class to load the NetsSchedule.html file into a character vector in R. Call the vector nets1617.
a. How many lines are in the NetsSchedule.html file?
```{r}
hw3 = "~/Desktop/2016 fall/5206/hw3/NetsSchedule.html"
nets = readLines(hw3)
length = length(readLines(hw3)); length

 # There are 811 lines in this html file. 
```
b. What is the total number of characters in the file?
```{r}
sum(nchar(nets))
# There are 127835 characters in the file.
```
c.What is the maximum number of characters in a single line of the file?
```{r}
max(nchar(nets))

# 7211 is the maximum number of characters in a single line of the file
```
#ii. Open NetsSchedule.html as a webpage.
Who and when are they playing first? Who and when are they playing last?
```{r}
#The first game: Wed, Oct 26 7:30 PM, opponent is Boston 
#The last game:Wed, Apr 12 8:00 PM, opponent is Chicago.
```
iii. Now, open NetsSchedule.html using a text editor.
```{r}
#The first line of the schedual provides the infomation of the first game.
# The last line of the schedual provides the infomaiton of the last gaeme.
```
iv. Write a regular expression that will capture the date of the game.
```{r}
team.lines = grep(pattern="0 PM", x=nets);team.lines
length(team.lines)
nets[315]
nets[397]

# The fist locations matches the game on Oct 26.
#The last location matches the game on April 12.
```
v. Using the expression  you wrote  in (v) along with the functions regexp() and regmatches(), extract the dates from the text file. Store this information in a vector called date to
save to use below.
```{r}
pattern <- "0 PM"
 m = regexpr(pattern, nets, perl=TRUE)
regmatches(nets,m)
```
vi. Use the same strategy as in (v) and (vi) to create a time vector that stores the time of the game.
```{r}
pattern = "0 PM"
m <- regexpr(pattern, nets)
regmatches(nets, m)
```
vii. We would now like to gather information about whether the game is home or away.
```{r}
pattern = "@"
m <- regexpr(pattern, nets)
regmatches(nets, m)
pattern1 = "vs"
m <- regexpr(pattern1, nets)
regmatches(nets, m)
```
viii. Finally we would like to find the opponent
```{r}
pattern = "@"
m <- regexpr(pattern, nets)
opponent = regmatches(nets, m)
```