---
title: "HW9a"
author: "Autumn Li"
date: "12/4/2016"
output: pdf_document
---
#Part I
#1
(a) How many doctors began prescribing tetracycline in each month of the study? (b) How many never prescribed it? (c) How many are NAs?
```{r}
ckm_nodes.1 <- read.csv("~/Desktop/ckm_nodes-1.csv")
ckm= ckm_nodes.1
date = ckm$adoption_date
na = length(date[date =="NA"]);na
never = length(na.omit(date[date =="Inf"]));never
begin = length(date)- length(date[date =="NA"]) - length(na.omit(date[date =="Inf"]));begin
```
(a)There are 109 doctors begin prescribing tetracyline in each month of the study;(b)There are 16 doctors never prescribing it.(c) There are 121 NA.

2. Create a vector which records the index numbers of the doctors for whom adoption date is not NA.

```{r}
not.na = na.omit(date)
ind_na = which(is.element(date=="NA",date))
vect = 1:246
dr_ind = vect[-ind_na]

```
3. Create a plot of the number of doctors who began prescribing tetracycline each month versus time.
```{r}
ind_inf = which(is.element(not.na=="Inf",not.na))
dr_num = not.na[-ind_inf]
dr_num = sort(dr_num);dr_num
count2 = NULL
i=1
while(i <= max(dr_num)){
  count1 = NULL
  for(k in 1:length(dr_num)){
    if(dr_num[k] == i){
      count1[k] = 0
      } 
    }
  count2[i] = length(na.omit(count1))
    i = i +1 
  }
count2


ind_inf = which(is.element(not.na=="Inf",not.na))
dr_num = not.na[-ind_inf]
dr_num = sort(dr_num);dr_num
count3 = NULL
count4 = NULL
i=1
while(i <= max(dr_num)){
  for(k in 1:length(dr_num)){
    if(dr_num[k] == i){
      count4[k] = 0
      } 
    }
  count3[i] = length(na.omit(count4))
    i = i +1 
  }
count3
par(mfrow=c(1,2))
plot(time,count2)
plot(count3)
```
4.Create a logical vector which indicates for each doctor whether they had begun pre- scribing tetracycline by month 2. 
```{r}
logic = NULL
for(i in 1:length(not.na)){
  if(not.na[i]<=2) {
    logic[i] = 0
    }
  }
vect1 = 1:length(logic)
ind_m2 = vect1[-which(is.element(logic == 0,logic))]
length(ind_m2)

logic2 = NULL
for(i in 1:length(not.na)){
  if(not.na[i]>14) {
    logic2[i] = 0
    }
  }
vect2 = 1:length(logic2)
ind_m14 = vect2[-which(is.element(logic2 == 0,logic2))]
length(ind_m14)

```
#Part II
5. 
```{r}
ckm_network.1 <- read.table("~/Desktop/ckm_network-1.txt", quote="\"")
ckm_txt = ckm_network.1 
dim(ckm_txt)
network = ckm_txt[-ind_na,-ind_na]
dim(network)

```
6. Create a vector which stores the number of contacts each doctor has. Do not use a loop. Check that doctor number 41 has 3 contacts.
```{r}
apply(network,1,sum)[41]
```
7.
```{r}
nodes = read.csv("~/Desktop/ckm_nodes-1.csv")
date = nodes$adoption_date
not.na = na.omit(date)
ind_na = which(is.element(date=="NA",date))
vect = 1:246
dr_ind = vect[-ind_na]
nodes = nodes[dr_ind,]
doctor_37 = network[,37]
m = sum(nodes$adoption_date <= 5 * network[,37])
propotion = m/sum(network[,37])
propotion

```
